5_data_viz

### 2018-05-30 scripts/5_data_viz.Rmd
Image updates

  png(filename = file.path(getwd(), 'images', "block_rate_hist.png"), 
       width = 5.5, height = 4, units = 'in', res = 300)

    ggplot(str_tdf, aes(x=block_rate)) + 
      geom_density(fill=str_col, color=str_col) +
      ylab('Frequency\n') + 
      xlab('\n% of Time Property is Blocked') +
      scale_x_continuous(breaks=seq(0,1,.2),
                         labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
        ggtitle('Host Block Rate Frequency\n') +
        theme(plot.title = element_text(hjust = 0.5)) +
        theme(axis.text.y=element_blank(),
              axis.ticks.y=element_blank())

  png(filename = file.path(getwd(), 'images', "block_periods_scat.png"), 
       width = 5.5, height = 4, units = 'in', res = 300)

  ggplot(str_tdf, aes(x=block_rate, y=nbr_block * (366/total_days))) + 
    geom_point(fill=str_col, color=str_col, size=.2) +
    ylab('Nbr of Blocked Periods\n') + 
    xlab('\n% of Time Property is Blocked') +
    scale_x_continuous(breaks=seq(0, 1, .2),
                       labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
    theme(plot.title = element_text(hjust = 0.5))

  png(filename = file.path(getwd(), 'images', "host_type_scat.png"), 
       width = 5.5, height = 4, units = 'in', res = 300)

   ggplot(str_tdf, 
          aes(x=block_rate, y=blockpertime, color=host_type)) + 
     geom_point(alpha=.5, size=.8, shape=16) +
     ylab('Number of Blocked Periods\n') + 
     xlab('\n% of Time Property is Blocked') +
        ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +

      scale_x_continuous(breaks=seq(0, 1, .2),
                       labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
      scale_color_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[7], 
                                  col_df$rgb[9])) + 
      theme(legend.position='bottom',
           legend.title = element_blank(),
         plot.title = element_text(hjust = 0.5))+
       guides(colour = guide_legend(override.aes = list(size=3,
                                                     alpha=1)))

@@

>>>>

  str.col <- col_df$rgb[1]

  ## Create table of host block frequencies

  host.block.freq <- ggplot(str_tdf, aes(x=block_rate)) +
     geom_density(fill=str.col, color=str.col) +
     ylab('Frequency\n') +
     xlab('\n% of Time Property is Blocked') +
     scale_x_continuous(breaks=seq(0,1,.2),
                        labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
     #ggtitle('Host Block Rate Frequency\n') +
     theme(plot.title = element_text(hjust = 0.5)) +
     theme(axis.text.y=element_blank(),
           axis.ticks.y=element_blank())

  block.rate.period <- ggplot(str_tdf, aes(x=block_rate, y=nbr_block * (366/total_days))) +
    geom_point(fill=str.col, color=str.col, size=.2) +
    ylab('Nbr of Blocked Periods\n') +
    xlab('\n% of Time Property is Blocked') +
    scale_x_continuous(breaks=seq(0, 1, .2),
                       labels=c('0%', '20%', '40%', '60%', '80%', '100%')) +
    #ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
    theme(plot.title = element_text(hjust = 0.5))

    png(filename = file.path(getwd(), 'images', "block_rate.png"), 
       width = 5.5, height = 3, units = 'in', res = 300)

       ggMultiPlots(host.block.freq, block.rate.period, cols=2)

@@

```{r host_types2}

  base.host <- ggplot(str_tdf,
                    aes(x=block_rate, y=blockpertime)) +
                geom_point(alpha=.7, size=.4, shape=16, color='gray70') +
                ylab('# Blckd Periods\n') +
                xlab('\n% of Time Property is Blocked') +
                ggtitle('Block Rate vs. Nbr. of Blocked Periods\n') +
                scale_x_continuous(breaks=seq(0, 1, .2),
                                   labels=c('0%', '20%', '40%',
                                            '60%', '80%', '100%')) +
                #scale_color_manual(values=c(abb.col[2], abb.col[4],
                #                            abb.col[7], abb.col[9])) +
                theme(legend.position='bottom',
                      legend.title = element_blank(),
                      plot.title = element_text(hjust = 0.5))+
                guides(colour = guide_legend(override.aes = list(size=3,                                                                       alpha=1)))

   ps.host <- base.host +
    geom_point(data=str_tdf[str_tdf$host_type == 'Profit Seeker', ], size=.4)  +
    ggtitle('Profit Seekers')

  os.host <- base.host +
    geom_point(data=str_tdf[str_tdf$host_type == 'Opportunistic Sharer', ],
               size=.4)  +
    ggtitle('Opportunistic Sharer')

  mu.host <- base.host +
    geom_point(data=str_tdf[str_tdf$host_type == 'Multi-Platform User', ],
               size=.4)  +
    ggtitle('Multi-Platform User')

  un.host <- base.host +
    geom_point(data=str_tdf[str_tdf$host_type == 'Unknown', ], size=.4)  +
    ggtitle('Unknown')

  png(filename = file.path(getwd(), 'images', "host_scat.png"), 
       width = 5.5, height = 3, units = 'in', res = 300)

    ggMultiPlots(ps.host, mu.host, os.host, un.host, cols=2)

```{r plot_hostbar, message=FALSE, warning=FALSE, comment=FALSE, echo=FALSE, fig.height=3, fig.width=4, fig.cap='\\label{htc}Host Type Counts'}

 ## Build plot

  png(filename = file.path(getwd(), 'images', "host_bar.png"), 
       width = 3, height = 3, units = 'in', res = 300)

 ggplot(str_tdf, aes(host_type, fill=host_type)) +
    geom_bar() +
    scale_fill_manual(values=c(col_df$rgb[2], col_df$rgb[4], col_df$rgb[7], 
                               col_df$rgb[9]))+
    theme(legend.position='none') +
    ylab('Frequency\n') +
    xlab('\nHost Type') +
    scale_x_discrete(labels=c('Profit','Sharer','Multi','Unknown'))+
    #ggtitle('short-term Host Types') +
    theme(plot.title = element_text(hjust = 0.5))
